---
title: "LeanTaas"
author: "Aadish Chopra"
date: "9/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r warning=FALSE,message=FALSE}
source("bootstrap.R")

# connect to the sqlite file
sqlite    <- dbDriver("SQLite")
LTDB <- dbConnect(sqlite,"LeanTaaSTestDB.db")
LT_table<-dbListTables(LTDB)
statement<-paste0("Select * from ",LT_table)

# get data in a dataframe

exchange_transc<-dbGetQuery(conn = LTDB,statement = statement)
dbDisconnect(LTDB)

# to analyze the file outside of tableau
#write.csv(exchange_transc,"exchange_transactions.csv")


```



```{r}
exchange_transc$created_date<-as_date(exchange_transc$created_datetime)
exchange_transc$created_time<-substr(exchange_transc$created_datetime,12,19)
exchange_transc$snapshot_date<-as_date(exchange_transc$snapshot_date)
exchange_transc$start_time<-parse_hms(exchange_transc$start_time)
exchange_transc$end_time<-parse_hms(exchange_transc$end_time)
exchange_transc$created_time<-parse_hms(exchange_transc$created_time)
```


Following visualization would help us in giving an idea of how the exchange system is being used. 

```{r fig.width=10}

exchange_transc %>% group_by(action) %>% summarise(count=n()) %>% ggplot(.,mapping = aes(x=action,y=count,fill=action))+geom_bar(stat = 'identity')+theme(axis.text.x = element_text(angle = 90, hjust = 1))+geom_text(aes(label=count), position=position_dodge(width=0.9), vjust=-0.25)

```


# Analyzing the transactions


#### Analyzing request transactions

```{r}

kable(exchange_transc %>% filter(action %in% c('REQUEST','APPROVE_REQUEST','DENY_REQUEST')) %>% count(action),caption = "Breakdown for transactions of type Request",col.names = c('action','count'))



request_transactions<-exchange_transc %>% filter(action %in% c('REQUEST'))
getChildId<-function(parentid)
{
  child_ids<-exchange_transc[exchange_transc$parent_transaction_id %in% parentid,]
  child_ids<-child_ids %>% filter (action %in% c('APPROVE_REQUEST','DENY_REQUEST'))
  parent_transaction<-request_transactions[request_transactions$transaction_id %in% parentid,]
  time_to_resolve<-difftime(child_ids[,"created_date"],parent_transaction[,"created_date"])
  return (time_to_resolve)
}

ttr<-unlist(lapply(request_transactions$transaction_id, getChildId))



```


> The mean response rate to either deny or approve a **REQUEST** transaction is `r mean(ttr)` days

#### Analyzing transfer transactions

```{r}

transfer_transactions<-exchange_transc %>% filter(action %in% c('TRANSFER'))
get_tr_ChildId<-function(parentid)
{
  child_ids<-exchange_transc[exchange_transc$parent_transaction_id %in% parentid,]
  child_ids<-child_ids %>% filter (action %in% c('APPROVE_TRANSFER','DENY_TRANSFER'))
  parent_transaction<-transfer_transactions[transfer_transactions$transaction_id %in% parentid,]
  time_to_resolve<-difftime(child_ids[,"created_date"],parent_transaction[,"created_date"],units = "days")
  return (time_to_resolve)
}


ttt<-unlist(lapply(transfer_transactions$transaction_id, get_tr_ChildId))




```

> The mean response rate to either deny or approve a **TRANSFER** transaction is `r mean(ttt)` days

#### Analyzing Release transactions

```{r}
release_transactions<-exchange_transc %>% filter(action %in% c('RELEASE'))
get_rs_ChildId<-function(parentid)
{
  child_ids<-exchange_transc[exchange_transc$parent_transaction_id %in% parentid,]
  child_ids<-child_ids %>% filter (action %in% c('MARK_UPDATED','DENY_RELEASE'))
  parent_transaction<-release_transactions[release_transactions$transaction_id %in% parentid,]
  time_to_resolve<-difftime(child_ids[,"created_date"],parent_transaction[,"created_date"],units = "days")
  return (time_to_resolve)
}


trt<-unlist(lapply(release_transactions$transaction_id, get_rs_ChildId))
mean(trt)


```

> The mean response rate to either update a **RELEASE** transaction is `r mean(trt)` days


Request and Transfer transactions will be broken down in later sections of the report



#### Number of locations in logs

Assumption: 1. Each location is not the same as every other location
            2. Each room within a location is same as every other room


```{r}

kable(unique(exchange_transc$location),col.names = 'location')

```


```{r}

kable(exchange_transc %>% group_by(location) %>% summarise(count=n()) %>% arrange(desc(count)))
kable(exchange_transc %>% group_by(location,room_name) %>% summarise(count=n()) %>% arrange(desc(count)))

```


#### Utilization of resources


```{r}

exchange_transc %>% group_by(location) %>% filter(action %in% c('APPROVE_REQUEST','APPROVE_TRANSFER')) %>% summarise(count=n(),occupiedtime=mean(difftime(end_time,start_time,units = "hours"))) %>% mutate(occupiedtime=as.numeric(sprintf("%0.2f",occupiedtime)))%>% ggplot(.,mapping = aes(x=reorder(location,-occupiedtime),y=occupiedtime,fill=location))+
geom_bar(stat='identity')+xlab('location')+ylab('avg. occupied time (hrs)')+ geom_text(aes(label=occupiedtime), position=position_dodge(width=0.9), vjust=-0.25)


```

Occupied time shows the average utilization of these resources 


#### Analysis of released resources

```{r}

exchange_transc %>% group_by(location) %>% filter(action %in% c('RELEASE')) %>% summarise(count=n(),releasetime=mean(difftime(end_time,start_time,units = "hours")))%>%
mutate(releasetime=as.numeric(sprintf("%0.2f",releasetime))) %>% ggplot(.,mapping = aes(x=reorder(location,-releasetime),y=releasetime,fill=location))+geom_bar(stat='identity')+xlab('location')+ylab('avg. release time (hrs)')+geom_text(aes(label=releasetime), position=position_dodge(width=0.9), vjust=-0.25)


```


#### Analyzing a location's daily usage pattern


```{r}
getUsagePattern<-function(location)
{
  filtered_locations<-exchange_transc[exchange_transc['location']==location,]
  filtered_locations<-filtered_locations[filtered_locations['action']=='APPROVE_TRANSFER'|filtered_locations['action']=='APPROVE_REQUEST',]
  plot(density(hour(filtered_locations[,'created_time'])),main = "Usage patterns for Approvals",xlim = c(0,24),xlab = "Hour")
  
  
}

getUsagePattern('CENTER')

```


```{r}


getUsagePattern<-function(location)
{
  filtered_locations<-exchange_transc[exchange_transc['location']==location,]
  filtered_locations<-filtered_locations[filtered_locations['action']=='REQUEST'|filtered_locations['action']=='TRANSFER',]
  plot(density(hour(filtered_locations[,'created_time'])),main = "Usage patterns for Requests and Transfers",xlim = c(0,24),xlab = "Hour")
  
  
}

getUsagePattern('CENTER')
  
```

