---
title: "LeanTaas"
author: "Aadish Chopra"
date: "9/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r warning=FALSE,message=FALSE}
source("bootstrap.R")

# connect to the sqlite file
sqlite    <- dbDriver("SQLite")
LTDB <- dbConnect(sqlite,"LeanTaaSTestDB.db")
LT_table<-dbListTables(LTDB)
statement<-paste0("Select * from ",LT_table)

# get data in a dataframe

exchange_transc<-dbGetQuery(conn = LTDB,statement = statement)
dbDisconnect(LTDB)

# to analyze the file outside of tableau
#write.csv(exchange_transc,"exchange_transactions.csv")


```



```{r}
exchange_transc$created_date<-as_date(exchange_transc$created_datetime)
exchange_transc$created_time<-substr(exchange_transc$created_datetime,12,19)
exchange_transc$snapshot_date<-as_date(exchange_transc$snapshot_date)


```


Following visualization would help us in giving an idea of how the exchange system is being used. 

```{r fig.width=10}

exchange_transc %>% group_by(action) %>% summarise(count=n()) %>% ggplot(.,mapping = aes(x=action,y=count,fill=action))+geom_bar(stat = 'identity')

```


# Analyzing the transactions


#### Analyzing request transactions

```{r}

exchange_transc %>% filter(action %in% c('REQUEST','APPROVE_REQUEST','DENY_REQUEST')) %>% count(action)



request_transactions<-exchange_transc %>% filter(action %in% c('REQUEST'))
getChildId<-function(parentid)
{
  child_ids<-exchange_transc[exchange_transc$parent_transaction_id %in% parentid,]
  child_ids<-child_ids %>% filter (action %in% c('APPROVE_REQUEST','DENY_REQUEST'))
  parent_transaction<-request_transactions[request_transactions$transaction_id %in% parentid,]
  time_to_resolve<-difftime(child_ids[,"created_date"],parent_transaction[,"created_date"])
  return (time_to_resolve)
}

ttr<-unlist(lapply(request_transactions$transaction_id, getChildId))
mean(ttr)

```

#### Analyzing transfer transactions

```{r}

transfer_transactions<-exchange_transc %>% filter(action %in% c('TRANSFER'))
get_tr_ChildId<-function(parentid)
{
  child_ids<-exchange_transc[exchange_transc$parent_transaction_id %in% parentid,]
  child_ids<-child_ids %>% filter (action %in% c('APPROVE_TRANSFER','DENY_TRANSFER'))
  parent_transaction<-transfer_transactions[transfer_transactions$transaction_id %in% parentid,]
  time_to_resolve<-difftime(child_ids[,"created_date"],parent_transaction[,"created_date"],units = "days")
  return (time_to_resolve)
}


ttt<-unlist(lapply(transfer_transactions$transaction_id, get_tr_ChildId))
mean(ttt)



```


#### Analyzing Release transactions

```{r}
release_transactions<-exchange_transc %>% filter(action %in% c('RELEASE'))
get_rs_ChildId<-function(parentid)
{
  child_ids<-exchange_transc[exchange_transc$parent_transaction_id %in% parentid,]
  child_ids<-child_ids %>% filter (action %in% c('MARK_UPDATED'))
  parent_transaction<-release_transactions[release_transactions$transaction_id %in% parentid,]
  time_to_resolve<-difftime(child_ids[,"created_date"],parent_transaction[,"created_date"],units = "days")
  return (time_to_resolve)
}


trt<-unlist(lapply(release_transactions$transaction_id, get_rs_ChildId))
mean(trt)


```

Request and Transfer transactions will be broken down in later sections of the report



#### Number of locations in logs

Assumption: 1. Each location is not the same as every other location
            2. Each room within a location is same as every other room


```{r}

unique(exchange_transc$location)

```


```{r}

exchange_transc %>% group_by(location) %>% summarise(count=n())
exchange_transc %>% group_by(location,room_name) %>% summarise(count=n())

```


#### Utilization of resources


```{r}

exchange_transc %>% group_by(location) %>% filter(action %in% c('APPROVE_REQUEST','APPROVE_TRANSFER')) %>% summarise(count=n(),occupiedtime=difftime(end_time,start_time))


```

